\opt{text}{\skbheading{Files and Headings}}

\DescribeMacro{\skbinput}
\DescribeMacro{\skbheading}
Just to remember: we have two different types of files in two
different directory structures. The repository folder stores the
content and the publish folder stores everything needed to produce
complete documents. For the content in the repository, we mark headings
with the macro \cmd{\skbheading}. This macro has no options and no arguments
and is simply called with the text for the heading, as shown in
\opt{text}{the following example.}\opt{note}{the first block on this slide.}

\opt{text}{
  \lstinputlisting[style=generic,language=TeX]{\skbfileroot{examples/skbheading}}
}

Leaving the argument empty will have the same effect as calling the original \LaTeX~
macros directly with an empty argument.

The association of a \LaTeX~document level with the heading is then defined 
for the published documents (in the publish folder) using the macro \cmd{\skbinput}.
This macro provides a number of options and requires one argument.
\opt{text}{The follwing examples}\opt{note}{The second block on this slide} shows
a few use cases for \cmd{\skbinput}.
\opt{text}{For all possible options, please see \autoref{tab:skbinput:options}}

\opt{text}{
  \lstinputlisting[style=genericLN,language=TeX]{\skbfileroot{examples/skbinput}}
}

\opt{text}{
  \begin{table}[ht!]
    \caption{Options for skbinput}
    \label{tab:skbinput:options}
    \begin{tabular*}{\textwidth}{ >{\small}p{.1\textwidth} >{\small}p{.40\textwidth} >{\small}p{.40\textwidth}}
      \toprule
      \textbf{Option} & \textbf{Description} & \textbf{Values} \\
      \midrule
      \skbinput[from=rep]{manual/skbinput-opt-table}
      \bottomrule
    \end{tabular*}
  \end{table}
}

Let's start with the simpliest form, one argument only shown in line 1.
The macro will look for a file called myfile.tex in the root directory of the \skbacft{A3DS:SKB}.
The file extension .tex is automatically added, and since we did not specify any
special directory the root directory is used instead.
If the file is not found, the macro will throw an error providing the full path and filename it
did try to load.

Line 2 shows how we can load the file \skbem[code]{myfile.tex} from the repository folder.
As you can see, the option \skbem[code]{from} is supplied with the argument \skbem[code]{rep},
which in fact directs the macro to look for \skbem[code]{myfile.tex} in the repository folder.
Should the file be located in the folder for published documents, we simply change the 
\skbem[code]{from} option to \skbem[code]{pub} as shown in line 3.

If \skbem[code]{from} is used and neither \skbem[code]{pub} nor \skbem[code]{rep} is given, the macro will trow an error.

To associate a document level for the heading, we can use the option \skbem[code]{level} to define which 
level we want. This option understands all standard document levels from the memoir package: book, part, 
title, chapter, section, subsection and subsubsection. So, if we want to load myfile.tex as a chapter 
we simple invoke \cmd{\skbinput} as shown in line 4 of the example.

Since myfile.tex is part of the repository,
we combine the two options \skbem[code]{from} and \skbem[code]{level} (see line 5).
This call to \cmd{\input} will load \skbem[code]{myfile.tex} from the repository and use \cmd{\chapter} for 
the heading found in that file. If \skbem[code]{myfile.tex} is in a sub folder, we simply add that sub folder to 
the filename. An example is shown in line 6 assuming the the file is located in the repository sub-folder 
examples.
