\skbheading{The SKB Documentation}

The documentation of this package is using most macros the \skbacft{A3DS:SKB} defines, thus 
realising two things in one go: it provides the documentation for the package showing
its features and it is used to test the the packge while generating the documentation
(I might say that we do other tests as well). With all that, it can now be also used
as one example on how to maintain a document repository, and that's exactly what the 
following statements trying to achieve.

As we have seen earlier, the \skbacft{A3DS:SKB} documentation comes in several parts. First, there 
is the documentation on the documented \LaTeX~source code (skb.dtx). Next, there is 
the user guide, which can be compiled along with the documented source (see skb.pdf)
or as a stand-alone article document (see user-guide.pdf). Since we use our \skbacft{A3DS:SKB} for
presentations, we provide an animated and a non-animated presentation about the \skbacft{A3DS:SKB}
(ug-slides-anim.pdf and ug-slides-noanim.pdf) along with annotated slides as a handout
(ug-slides-notes.pdf). All of these documents use the same source, which includes
some conditional text. All of these documents `assemble' their content in their specific way
which quits their purpose best. For instance, the document level are different for the
headings, the text blocks and tables and figures and examples are ordered in different
way and some text is incuded in one \skbacft{ISO:PDF} document and not in others.




The documentation has three main parts. The first tells some stories and 
explains the general concepts of the \skbacft{A3DS:SKB}. This part is generated using
many \skbacft{A3DS:SKB} macros including \cmd{\skbinput} and \cmd{\skbheading}.
The second part documents the implementation of the \skbacft{A3DS:SKB} package. This part
uses only some macros for the layout. The last part provides information
about the history of the package and a change log. This part again uses 
\cmd{\skbinput} and \cmd{\skbheading} and many other \skbacft{A3DS:SKB} macros.

Let's start with the first part, of which this example is again a part of.
The \skbacft{A3DS:SKB} documentation is split over two main directories: \skbem[code]{publish}
for the actual article and \skbem[code]{repository}. The folder \skbem[code]{publish/article/tex}
contains two files, the fiel with the title page of the aticle \skbem[code]{skb.tex} and one for loading the
repository files \skbem[code]{contents.tex} and creating the intended document structure (levels).
The file \skbem[code]{user-guide.tex} looks like as follows:

\lstinputlisting[style=genericLN,language=TeX]{\skbfilepub{article/tex/skb-titlepage}}

Line by line the macros calls here have the following effect:
\begin{skbnotelist}
  \item Line 1\&2 set the title for the document.
  \item Line 4 sets the author of the document.
  \item Line 6 sets the date and version information for the document.
  \item Line 8\&9 use the \skbacft{A3DS:SKB} macros \cmd{\skbsubject} and \cmd{\skbkeywords} to set the subject
        and keywords for \skbacft{ISO:PDF} info.
  \item Line 11 calls \cmd{\maketitle} to create the title minipage (we are in an article class).
  \item Line 13\&15 start and finish the abstract.
  \item Line 21 finished the \TeX processing of the file by calling \cmd{\endinput}.
\end{skbnotelist}

The interesting lines here are number 14 and 19. They use the \skbacft{A3DS:SKB} macro \cmd{\skbinput} to load 
further content. In line 14 it is a file called \skbem[code]{abstract.tex} from the repsitory.
Note: \cmd{\skbinput} automatically adds the file extension \skbem[code]{.tex} when loading from the repository or publish folders.
Now the file \skbem[code]{abstract.tex} contains the one paragraph abstract of this document. Nothing else
special in there.

The other file in  the folder \skbem[code]{publish/article/tex} -- \skbem[code]{skb-contents.tex} -- will actually load
all other files required to build the first part of this document and create the intended document structure
(i.e. sections and subsections). This file looks like this:

\lstinputlisting[style=genericLN,language=TeX]{\skbfilepub{article/tex/skb-contents}}

The first line uses the classic \LaTeX macro \cmd{\section} to start the section \skbem[italic]{Introduction}.
All other lines use the \skbacft{A3DS:SKB} macro \cmd{\skbinput} to load files from the repository and associate a \LaTeX document
level to them. In the case of this document we use sections, subsections and subsubsections. Each of the files loaded here
with \cmd{\skbinput} will start by calling the \skbacft{A3DS:SKB} macro \cmd{\skbheading} to declare the heading text. For instance, the
first few lines of the file \skbem[code]{separate-parts.tex} in the repository (loaded in line 7) look like this
(we show the first 4 lines):

\lstinputlisting[style=genericLN,language=TeX,lastline=4]{\skbfilerep{separate-parts}}

In other words: line 7 of \skbem[code]{contents.tex} calls \cmd{\skbinput} with the option \skbem[code]{from} set 
ro \skbem[code]{rep} and the option \skbem[code]{level} set to \skbem[code]{subsection} and requests to load a file 
called \skbem[code]{separate-parts.tex}. This loaded file then first calls \cmd{\skbheading} to declare a heading text.
The \skbacft{A3DS:SKB} now will translate use heading tex calling the classic \LaTeX macro \cmd{\subsection}. The rest is done by
\LaTeX as usual.

If you have a look into the directory \skbem[code]{source/repository} of this distribution, you will see all tex files 
that form part one of this document. You will also see that parts of the documentation, namely code and dirtree figures,
have been separated out in sub-directories.

Finally, the file \skbem[code]{skb.dtx} uses the \skbacft{A3DS:SKB} macro \cmd{\skbinput} to load the files \skbem[code]{skb-titlepage.tex}
and \skbem[code]{skb-contents.tex} from the publish folder. You can find that macro call just above \cmd{\StopEventually}
in \skbem[code]{skb.dtx}. Furthermore, if you look at the very end of \skbem[code]{skb.dtx}, just above \cmd{\Final}, you
will find the call to \cmd{\skbinput} that loads the file \skbem[code]{history.tex} from the repository.